Finite-state morphological transducers for three Kypchak languages

### 2013-10-14 kipchak-lrec-2013/kipchak-paper.tex
more
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48082 72bbbca6-d526-0410-a7d9-f06f51895060

We would like to thank the Google Code-in (2011) for supporting the development 
of the Kazakh transducer and the Google Summer of Code (2012) for supporting the 
development of both the Kazakh and the Tatar transducers.

>>>>

We would like to thank the Google Code-in (2011) for supporting the development 
of the Kazakh transducer, and in particular the effort by Nathan Maxson. We 
would also like to thank the Google Summer of Code (2012) for supporting the 
development of both the Kazakh and the Tatar transducers.
